Model Search in Relational Domains

### 2016-10-23 conclusion.tex
conclusion

\section{Conclusions}
In this paper, we present a procedure for lifting the model search 
in satisfiability solvers to relational abstract domains.  
%We explain specific properties of abstract domain elements that are necessary to infer domain-specific deductions.  
We present a parameterised abstract transformer that allows us to
flexibly implement various propagation heuristics while taking care of
the closure operation required in relational abstract domains.
%
Our decision heuristics take into account the high-level structure of
programs and the underlying expressivity of the abstract domains.  Our
conflict analysis procedure learns abstract transformers following a
UIP computation over relational domain elements.  We instantiate our
algorithms as a program analyser to determine safety of C programs.
%
Experimental evaluation shows that ACDCL is able to suitably exploit the
expressivity of richer abstract domains as well as the precision of the 
CDCL architecture.

>>>>

\section{Conclusions}
In this paper, we present a procedure for lifting the model search 
and conflict analysis procedures in satisfiability solvers for 
relational abstract domains.  
%We explain specific properties of abstract domain elements that are necessary to infer domain-specific deductions.  
We present a parameterised abstract transformer that allows us to
%flexibly implement various propagation heuristics while taking care of
flexibly guide the deductions in the abstract domain while performing lazy 
closure operations in the relational domains for efficiency reasons.
%
Our decision heuristics take into account the high-level structure of
programs and the underlying expressivity of the abstract domains.  Our
conflict analysis procedure learns abstract transformers following a
UIP computation over relational domain elements.  We instantiate our
algorithms as a program analyser to determine safety of C programs.
%
Experimental evaluation shows that ACDCL is able to suitably exploit the
expressivity of richer abstract domains as well as the precision of the 
CDCL architecture.
